%29.09.16
\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, amsthm, epsfig}

\newenvironment{definition}{\vspace{2 ex}{\noindent{\bf Definition}}}
        {\vspace{2 ex}}
\newenvironment{ques}{\vspace{2 ex}}{\vspace{2 ex}}


\theoremstyle{definition}

\newenvironment{Proof}{\noindent {\sc Proof.}}{$\Box$ \vspace{2 ex}}
\newtheorem{Wp}{Writing Problem}
\newtheorem{Ep}{Extra Credit Problem}
\renewcommand{\theenumi}{\alph{enumi}}

\oddsidemargin-1mm
\evensidemargin-0mm
\textwidth6.5in
\topmargin-15mm
%\headsep25pt
\textheight8.75in
\footskip27pt

\pagestyle{empty}
\begin{document}

\noindent \textit{\textbf{Math 380a, Fall 2016}} \hspace{1.3cm}
\textit{\textbf{HOMEWORK $\#$9}} \hspace{1.3cm} \textit{\textbf{Peter
Gylys-Colwell}} 

\vspace{1cm}

\begin{ques}
	\textbf{1.} 
		I will say the cliff is to the right of the drunk for convention
		\begin{enumerate}
			\item
				If we let $X(p)$ be the probablity that the drunk
				will eventually end up one square to his left
				(and fall from his original position) we have
				$X(p) = X(p) + (1-p)X(p)^2$ since there is a $X(p)$
				probablity he will just step right and fall,
				otherwise he will step left with probablity
				$(p-1)$ and from there can end up back where he
				started with probablity $X(p)$ and end up off the
				cliff with probablity $X(p)$ again. Therefore
				solving the quadratic we have  $X(p)$
				is either $1$ or $\frac{p}{1-p}$. We know with
				$p = 1$, $X(1) = 1$ and with $p = 0$, $X(0) =
				0$. Assuming $X(p)$ is a continuous function of
				$p$, it would follow that 
				$$X(p) = \begin{cases}
					1 & \frac{1}{2} \leq p \leq 1\\
					\frac{p}{1-p} & 0 \leq p \leq
					\frac{1}{2}
				\end{cases}$$
				Since $1 = \frac{p}{1 - p}$ at $p =
				\frac{1}{2}$ and from the bounds established at
				$p=0, p= 1$ we know what $X(p)$ will be on
				either side of $\frac{1}{2}$
			\item
				We can reduce the number of different paths he
				can take to fall on precisely the $k$th step ($P_k$)
				to a recursive formula based on previous steps.
				$$P_k = P_1P_{k-2} + P_3P_{k-4} +
				\dots P_{k-2}P_1$$
				The explination for this recursision formula is
				because after he takes his first step to the
				left, we can look at the number of ways he can
				first return to his original position. There
				are $P_i$ ways he first returns on precisely
				the $i$th step, once he is there, he has $k-i - 1$
				steps remaining and so there are precisely
				$P_{k-i - 1}$ ways for him to fall on the $k$th
				step, now we just sum up all these ways. Notice
				that $P_k$ is $0$ if $k$ is even since his
				displacement from his original position to the
				cliff is an odd number of steps and an even
				total number of steps would result in an even
				displacement.\\
				This recersive form is equivalent to the
				Catalyn numbers defenition with some
				reindexing: $C_k = P_{2k - 1}$. Catalyn numbers
				have the closed form
				$$P_k = C_{(k+1)/2} =
				\frac{1}{(k+1)/2+1}\binom{2(k+1)/2}{(k+1)/2} =
				\frac{1}{k/2 + 3/2}\binom{k+1}{(k+1)/2}$$
				We know that in total he must take $\frac{k +
				1}{2}$ steps right and $\frac{k-1}{2}$ steps
				left, so the total probablity of falling after $k$ steps is
				$$\frac{1}{k/2 + 3/2}\binom{k+1}{(k+1)/2}
				p^{\frac{k+1}{2}}(1-p)^{\frac{k-1}{2}}$$
		\end{enumerate}

\end{ques}

\begin{ques}
	\textbf{2.}  %donnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnne
		We can simply integrate the density of $1$ over the area of the
		regions where if the center of the coin landed, the coin would
		be inside a square, and divide by the total area of the chess
		board. $C$ has $8 \times 8$ squares, so $64$ squares,
		each $d^2$ area so $64d^2$ area total. There is a small square
		with side length $d - a$ sharing the center point of each
		square of $C$ such that if the center of the coin lands in any of these
		squares, the coin would be contained entirely in a square of
		$C$. If the center of the coin is not in one of these squares,
		it will intersect with the boundary of one of the squares of
		$C$. There are $64$ of these squares, so the total area the
		coin's center can land on is $64(d-a)^2$. So the probability is 
		$$\frac{64(d-a)^2}{64d^2} = \frac{(d-a)^2}{d^2}$$

\end{ques}

\begin{ques}
	\textbf{3.}  %donnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnne
		We have already established in class that the expected value of
		the minimum of a set of $n$ random numbers in $[0, 1]$ is
		$\frac{1}{n+1}$. If we shift all the values over by $-1$, we would
		shift the expected value by $-1$ as well and it would be the
		expected value of the min of the $n$ terms in $[-1, 0]$. And
		finally if we multiply each term by $-1$, we would multiply the
		expected value by $-1$, and we would be measureing the maximum
		value of the $n$ terms in $[0,1]$, which is what we want.
		Therefore our expected value is 
		$$-(\frac{1}{n+1} - 1) = 1 - \frac{1}{n+1} = \frac{n}{n+1}$$

\end{ques}

\begin{ques}
	\textbf{4.}   %donnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnne
		For a given $P$, the probablity that our rectangle is inside
		$C$ is the area of the rectangle inscribed in $C$ with one of
		the corners being $P$ and its sides parallel to the axis
		divided by the area of the whole circle. Any
		$Q$ outside of this rectangle would create a rectangle that has
		a side that extends beyond the bounds of $C$ and any $Q$ inside
		this rectangle would create a rectangle contained in the
		inscribed rectangle which is contained in $C$. Therefore to
		find the whole probability, we can integrate uniformly over the
		domain of $P$ the areas of these inscribed rectangles divided
		by the area of $C$ and divided by the arclength we are
		integrating over. Using polar coordinates we have
		$$\frac{1}{2\pi}\int_{0}^{2\pi} \frac{|2\cos(\theta)2\sin(\theta)|}{\pi} \ d
		\theta = \frac{1}{2\pi}4\int_{0}^{\pi/2}
		\frac{4\cos(\theta)\sin(\theta)}{\pi} \ d \theta$$
		Using a u-substitution for $u = \sin(\theta), du =
		\cos(\theta)$:
		$$= \frac{4}{2\pi}\frac{4\sin^2(\pi/2)}{2\pi} = \frac{4}{\pi ^ 2}$$
\end{ques}

\begin{ques}
	\textbf{EC.}  %donnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnne
		We simulate in the following way. We flip the coin twice if the
		coin pattern is $H,T$ then we say our balanced coin result
		would be $T$, if the pattern is $T,H$ then we say $H$. Any
		other pattern and we ignore it and repeat the process. We have
		that the probablity of $H, T$ is $p(1-p)$ while the probablity
		of $T,H$ is $(1-p)p$, and so the probabilities are equal,
		therefore we are simulating a balanced coin. We know that this
		process must terminate since the probablility of not
		terminating after $n$ times is $(2(1-p)p)^n = (2(p - p^2))^n <
		1^n$ and so as $n \to \infty$, $(2(1-p)p)^n \to 0$. (The reason
		$2(p - p^2) < 1$ is because the function $f(x) = x - x^2$ on
		$[0,1]$ is $<\frac{1}{2}$, we can use the derivative to find
		the critical point at $\frac{1}{2}$ to conclude this)

\end{ques}
\end{document}
