\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, amsthm, epsfig}

\newenvironment{definition}{\vspace{2 ex}{\noindent{\bf Definition}}}
        {\vspace{2 ex}}

\newenvironment{ques}[1]{\textbf{Exercise #1}\vspace{1 mm}\\ }{\bigskip}

\renewcommand{\theenumi}{\alph{enumi}}

\theoremstyle{definition}

\newenvironment{Proof}{\noindent {\sc Proof.}}{$\Box$ \vspace{2 ex}}
\newtheorem{Wp}{Writing Problem}
\newtheorem{Ep}{Extra Credit Problem}

\oddsidemargin-1mm
\evensidemargin-0mm
\textwidth6.5in
\topmargin-15mm
\textheight8.75in
\footskip27pt


\renewcommand{\l}{\left }
\renewcommand{\r}{\right }

\newcommand{\R}{\mathbb R}
\newcommand{\Q}{\mathbb Q}
\newcommand{\Z}{\mathbb Z}
\newcommand{\C}{\mathbb C}

\newcommand{\s}{\sin}
\renewcommand{\c}{\cos}

\renewcommand{\t}{\theta}
\renewcommand{\a}{\alpha}

\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

\newcommand{\T}{\mathcal{T}}

\pagestyle{empty}
\begin{document}

\noindent \textit{\textbf{Math 441, Fall 2017}} \hspace{1.3cm}
\textit{\textbf{HOMEWORK $\#$6}} \hspace{1.3cm} \textit{\textbf{Peter
Gylys-Colwell}} 

\vspace{1cm}

\begin{ques}{\S 23, 3}
	We have that 
	$$A \cup \l(\bigcup A_\a \r) = \bigcup \l( A \cup A_\a \r)$$
	We know that $A \cap A_\a$ is nonempty for each $\a$ so from Thm 23.3 each
	$A \cup A_\a$ is connected. Since $A$ is nonempty we have that there
	exists $p \in A$ so
	$$p \in \bigcap \l( A \cup A_\a \r)$$
	Thus from thm 23.3 we know that 
	$$\bigcup \l( A \cup A_\a \r)$$
	is connected.
\end{ques}

\begin{ques}{\S 23, 5}
	If $X$ has the discrete topology and $A \subseteq X$ is a subspace with
	more than two points $a, b \in A$, $a \neq b$, we have the seperation $A =
	\{a\} \cup (A - \{a\}$ where $A - \{a\}$ is nonempty since $b \in A -
	\{a\}$. Both these sets are open since every subset of the discrete
	topology is open. It is clear that one-point sets are connected since in
	order for $\{x\} = U \cup V$ where $U \cap V = \emptyset$, either $U$ or
	$V$ must be empty.\\
	$\Q$ is totally disconnect since for any subspace $A \subseteq \Q$ with two
	points $a,b \in A$, since the irrationals are dense there exists an
	irrational $r \in [a,b]$, and thus we have the seperation 
	$$A = \l(A \cap (-\infty, r)\r) \cup \l(A \cap (r, \infty)\r)$$
\end{ques}

\begin{ques}{\S 23, 9}
	Let us choose a point $(x,y) \in (X \times Y) - (A \times B)$ where $x
	\notin A, y \notin B$. We define the set $T = (\{x\} \times Y) \cup (X
	\times \{y\})$. This set is connected since $\{x\} \times Y$, $X \times
	\{y\}$ are homeomorphic to $Y$ and $X$ respectively, and thus since the
	intersection of these sets is $(x,y)$ (nonempty) from thm 23.3, $T$ is
	connected. \\ Now for any $(a,b) \in (X \times Y) - (A \times B)$ we have
	that either $a \notin A$ or $b \notin B$. Therefore we have that $T_a = \{a\}
	\times Y$ or $T_b = X \times \{b\}$ is contained in $(X \times Y) - (A \times
	B)$. Define $T_{(a,b)}$ as one of these sets which is contained in $(X \times
	Y) - (A \times B)$. Letting $M = (X \times Y) - (A \times B)$, we have that
	$$M = \bigcup_{(a,b) \in M} T_{(a,b)}$$
	This is clear since every $(a,b) \in M$ is contained in a $T_{(a,b)}$ and
	every $T_{(a,b)}$ is contained in $M$. It is clear that each $T_{(a,b)}$ is
	connected since it is homeomorphic to $X$ or $Y$. Finally we have that for
	each $(a,b)$, $T_{(a,b)} \cap T = (x,b)$ or $(a,y)$ and thus is not empty.
	Therefore we can use problem 23.3 to conclude that $M$ is connected.
\end{ques}

\begin{ques}{\S 24, 1}
	(a) \ If there exists a homeomorphism $f$ from  $[0,1]$ or $(0,1]$ to
	$(0,1)$, then $f(1) = a$ for some $a \in (0,1)$. However then we have that
	$f$ restricted to $[0,1] / \{1\}$ and $(0,1] / \{1\}$ is a homeomorphism to
	$(0,1) / \{a\}$. However $[0,1] / \{1\}$ and $(0,1] / \{1\}$ are connected
	while $(0,a) \cup (a,1)$ is disconnected which is a contradiction since
	homeomorphisms conserve connectivity. Similarly if there exists a
	homeomorphism $f$ from $[0,1]$ to $(0,1]$ then we have that $f(0) \neq
	f(1)$ so we have either $f(0)$ or $f(1)$ $ \neq 1$. WLOG we will say $f(0)
	= a \neq 1$. Then we have that the restriction of $f$ from $[0,1] / \{0\}$
	to $(0,a)\cup (a,1]$ is a homeomorphism. However it does not preserve
	connectivity, which is a contradiction.\\
	(b) \ Let $X = (0,1)$, $Y = [0,1]$. We already know $X$ is not homeomorphic
	to $Y$. however $X$ is homeomorphic to any open interval contained in $Y$
	(we proved in lecture all open intervals of $\R$ are homeomorphic) and thus
	there exists an imbedding from $X$ to $Y$. Similarly we know $Y$ is
	homeomorphic to any closed interval in $X$ and thus there exists an
	imbedding from $Y$ to $X$\\
	(c) \ We have that if there exists a homeomorphism $f : \R^n \to \R$ then
	letting $a \in \R^n$ be the point where $f(a) = 0$ then the restriction $f
	: \R^n / \{a\} \to \R / \{0\}$. However we have that $\R / \{0\}$ is
	disconnected while $\R^n / \{a\}$ is not which is a contradiction. $\R^n /
	\{a\}$ is not disconnected since we can apply Exercise 23.9 with $X = \R$,
	$Y = \R$, $A = \{a_x\}$ and $B = \{a_y\}$
\end{ques}

\begin{ques}{\S 24, 2}
	We can define the continous map $g(x) = f(x) - f(-x)$. This is continous
	since it is the composition and sum of continous functions.\\
	Notice that $g(x) = 0 \Rightarrow f(x) = f(-x)$, and thus if we show $g$
	must equal zero at some point, we are done. Also notice that $g(x) =
	-g(-x)$. Since $g$ maps connected sets to contected sets, we have
	that the connected set $A = S^1 \cap \{x + iy \in \C, x \geq 0$ gets mapped to
	a connected set. Therefore we have that $g(i)$ is either positive or
	negative (or zero in which case we are done). Then $g(-i)$ is also in the
	image and the opposite sign of $g(i)$. Thus we have a positive value and a
	negative value in $g(A)$. If $0 \notin g(A)$ then we get the seperation $g(A)
	= (g(A) \cap (-\infty, 0)) \cup ((0, \infty) \cap g(A))$ which contradicts
	$g(A)$ being connected. Thus $0 \in g(A)$ so $f(x) = f(-x)$ for some $x \in
	A$.
\end{ques}

\begin{ques}{\S 24, 10}
	We have proven the general result for $\R^n$ in lecture. Therefore it is
	true for $n = 2$
\end{ques}
\end{document}
